---
title: "Refine the Cars Data"
author: "Amit Kapoor"
date: "5 July 2015"
output: html_document
---

# Refine the Data

Now that we have got the raw data. We need to do a number of clean ups to actually make it into a useful data frame format for doing our exploration.

```{r}
library(dplyr)
library(stringr)

df.messy <- read.csv("data/cars.spec.raw.csv", stringsAsFactors = FALSE)
str(df.messy)
```

Lets make this from long to wide format - mainly for the specs

```{r}
library(tidyr)
df.tidier <- df.messy %>%
             separate(spec, c("spec", "value"), ":")

# Understand the number of specs - only 56
df.tidier %>% 
  group_by(spec) %>%
  summarize(n()) %>%
  View()

df.tidy <- df.tidier %>%
           spread(spec, value)
```


Let's start with cleaning name to get brand names

```{r}
# Lets start with name 
df.tidy %>% 
  group_by(name) %>%
  summarize(n())

# There are 203 unique names, lets start with taking the first word as brand
# In base R:  first <- unlist(strsplit(string, split=" "))[1]
df.tidy$brand <- word(df.tidy$name, 1)
df.tidy %>% 
  group_by(brand) %>%
  summarize(n()) %>%
  View()

```

Now. lets get the price as a numeric feature - we need to remove "Price (INR)Rs. " and remove the commas and make it as numeric
```{r}
pr <- "Price (INR)Rs. "
len.pr <- str_length(pr)  # Can also use nchar()

df.tidy$price <- df.tidy$price %>% 
             str_sub(len.pr, nchar(df.tidy$price)) %>%
             str_replace_all(",", "") %>%
             as.numeric()
```

Now, lets get the body type - we need to remove "Body Type" and convert as factor

```{r}
bt <- "Body Type "
len.bt <- str_length(bt)  # Can also use nchar()

df.tidy$type <- df.tidy$type %>% 
             str_sub(len.bt, nchar(df.tidy$type)) %>%
             as.factor()
```



