---
title: "Refine the Cars Data"
author: "Amit Kapoor"
date: "5 July 2015"
output: html_document
---

# Refine the Data

Now that we have got the raw data. We need to do a number of clean ups to actually make it into a useful data frame format for doing our exploration.

```{r}
library(dplyr)
library(stringr)

df.messy <- read.csv("data/cars.spec.raw.csv", stringsAsFactors = FALSE)
str(df.messy)
```

Lets make this from long to wide format - mainly for the specs

```{r}
library(tidyr)
df.tidier <- df.messy %>%
             separate(spec, c("spec", "value"), ":")

# Understand the number of specs - only 56
df.tidier %>% 
  group_by(spec) %>%
  summarize(n())

df.tidy <- df.tidier %>%
           spread(spec, value)
```

Lets fix the names in the columns

```{r}
tidy.names = c("name", "model", "url", "price", "type", "abs", 
               "acc", "aircon", "audiostr", "audio", "bluetooth", "bumper",
               "boot", "fbrake", "rbrake", "cdplayer", "locking",
               "airfilter", "cruise", "doorajar", "dseatwarn", 
               "airbags", "ebd", "disp", "engtype", "ftrack","ftyres",
               "fullsys", "tank", "fuel",
               "wheelcaps", "weight", "clearance", "heater",
               "immobiliser", "kerb", "keyless", "power", "torque",
               "kmplc", "kmplh", "cylinder", "size", 
               "sunroof", "pairbags", "steering", "fpowerwin", 
               "rpowerwin", "rainwiper", "rtrack", "rtyres", "seat", 
               "speaker", "tilt", "speed", "traction", "trans", 
               "tubeless", "turning", "usb", "wheelbase", "brand")

names(df.tidy) <- tidy.names
str(df.tidy)
```


Let's start with cleaning name to get brand names

```{r}
# Lets start with name 
df.tidy %>% 
  group_by(name) %>%
  summarize(n())

# There are 203 unique names, lets start with taking the first word as brand
# In base R:  first <- unlist(strsplit(string, split=" "))[1]
df.tidy$brand <- word(df.tidy$name, 1)
df.tidy %>% 
  group_by(brand) %>%
  summarize(n()) %>%
  View()

```

Now. lets get the price as a numeric feature - we need to remove "Price (INR)Rs. " and remove the commas and make it as numeric
```{r}
pr <- "Price (INR)Rs. "
len.pr <- str_length(pr)  # Can also use nchar()

df.tidy$price <- df.tidy$price %>% 
             str_sub(len.pr, nchar(df.tidy$price)) %>%
             str_replace_all(",", "") %>%
             as.numeric()
```

Now, lets get the body type - we need to remove "Body Type" and convert as factor

```{r}
bt <- "Body Type "
len.bt <- str_length(bt)  # Can also use nchar()

df.tidy$type <- df.tidy$type %>% 
             str_sub(len.bt, nchar(df.tidy$type)) 

df.tidy %>%
  group_by(type) %>%
  tally() %>%
  View()

# Clean up the tags

# Remove non ASCII character
df.tidy$type <- iconv(df.tidy$type, "latin1", "ASCII", sub="")

df.tidy$type[df.tidy$type == "Hatchabck"] <- "Hatchback"
df.tidy$type[df.tidy$type == "hatchback"] <- "Hatchback"
df.tidy$type[df.tidy$type == "Hatchback‎"] <- "Hatchback"


df.tidy$type[df.tidy$name == "Audi Q7"] <- "MUV"

df.tidy$type[df.tidy$type == "Seadan"] <- "Sedan"
df.tidy$type[df.tidy$type == "Sedna"] <- "Sedan"
df.tidy$type[df.tidy$type == "Sedans"] <- "Sedan"
df.tidy$type[df.tidy$type == "Seadn"] <- "Sedan"
df.tidy$type[df.tidy$type == "Saloon"] <- "Sedan"
df.tidy$type[df.tidy$type == "Saloon Sedan"] <- "Sedan"
df.tidy$type[df.tidy$type == "Luxury Sedan"] <- "Sedan"
df.tidy$type[df.tidy$type == "Luxury"] <- "Sedan"


df.tidy$type[df.tidy$type == "VAN"] <- "MUV"
df.tidy$type[df.tidy$type == "Van"] <- "MUV"
df.tidy$type[df.tidy$type == "Cabriolet"] <- "Convertible"
df.tidy$type[df.tidy$type == "Sport Coupe"] <- "Convertible"
df.tidy$type[df.tidy$type == "Supercar"] <- "Convertible"
df.tidy$type[df.tidy$name == "Porsche Boxster"] <- "Convertible"

df.small <- subset(df.tidy, is.na(df.tidy$type))

```

```{r}
# Convert as numeric
df.tidy$kmplc <- as.numeric(df.tidy$kmplc)
df.tidy$kmplh <- as.numeric(df.tidy$kmplh)

df.tidy %>%
  group_by(kmplh) %>%
  tally() %>%
  View()

